---
output:
  github_document:
    html_preview: FALSE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 120)
```
# redoc - reversible R Markdown/MS Word documents.

Author: _Noam Ross_

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/noamross/redoc?branch=master&svg=true)](https://ci.appveyor.com/project/noamross/redoc)
<!-- badges: end -->
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![Build
Status](https://travis-ci.org/noamross/redoc.svg?branch=master)](https://travis-ci.org/noamross/redoc)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/noamross/redoc?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/noamross/redoc)
[![codecov](https://codecov.io/gh/noamross/redoc/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/noamross/redoc)
[![CRAN status](https://www.r-pkg.org/badges/version/redoc){data-external="1"}](https://cran.r-project.org/package=redoc)
<!-- badges: end -->


**redoc** is an experimental package to enable a two-way R-Markdown ⟷ Microsoft
Word workflow.  It is in early design phase. Testing and feedback is welcome!
Please look at [CONTRIBUTING.md](https://github.com/noamross/redoc/blob/master/.github/CONTRIBUTING.md) and the [design vignette](https://noamross.github.io/redoc/articles/redoc-package-design.md)
if you are interested in development.

## Installation

Install the **redoc** package with this command:

```{r install_me, eval = FALSE}
source("https://install-github.me/noamross/redoc")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
```

## Usage

**redoc** provides an R Markdown [output format] of `rdocx_reversible()`, built
on top of `rmarkdown::word_document()`.  You will typically call it via the 
YAML header in your R Markdown document.  You have the option of highlighting
the outputs (both chunk and inline) in the Word Document.

```yaml
---
output:
  redoc::rdocx_reversible:
    keep_md: TRUE
    highlight_outputs: TRUE
---
```

Word files that have been created by `rdocx_reversible()` ("redocs") can be reverted to
`.Rmd` with `undoc()`, _even after they are edited_.

```{r undoc}
library(redoc)
undoc(redoc_example_docx())
```

If the Word document has tracked changes, `undoc()` will, by default, convert
these to [Critic Markup syntax](http://criticmarkup.com/spec.php#thebasicsyntax).

Undoc'ing a redoc where chunk outputs have been deleted will restore the original
code chunks to the document, usually immediately after the previous chunk. If
chunk outputs are moved, code chunks move with them.  Inline code outputs that
are deleted are not restored.

Redocs also store the original `.Rmd` used to make thim internally, which can
be extracted and used to diff against the original.

```{r extact}
redoc_extract_rmd(redoc_example_docx())
```

## Contributing

Want have feedback or want to contribute? Great! Please take a look at the [contributing guidelines](https://github.com/noamross/redoc/blob/master/.github/CONTRIBUTING.md) before filing an issue or pull request. 

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/noamross/redoc/blob/master/.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

```{r cleanup, include = FALSE}
unlink(c("example.Rmd", "example.docx", "skeleton.Rmd", "skeleton.docx", "skeleton.original.Rmd"))
```

